(Re-)bridging the anatomy ontologies with SSSOM

### 2024-06-16 presentation.tex
Update license and add README.
The paper is published under CC-BY, so we'll use CC-BY for the
presentation as well. We add the copyright notices and the full text of
the CC-BY license.

Also add a minimal README.

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{tikz}

@@

  \begin{block}{\includegraphics[scale=.26]{ccbysa}\hspace{.2em}%
    2024 Damien Goutte-Gattat \texttt{<dpg44@cam.ac.uk>}}
    This presentation is released under the Creative Commons
    Attributions-ShareAlike 4.0 License.
  \end{block}

>>>>

% SSSOM/T and Uberon presentation
% © 2024 Damien Goutte-Gattat
% 
% This work is released under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% https://creativecommons.org/licenses/by/4.0/.
\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{tikz}

@@

  \begin{block}{\includegraphics[scale=.26]{ccby}\hspace{.2em}%
    2024 Damien Goutte-Gattat \texttt{<dpg44@cam.ac.uk>}}
    This presentation is released under the Creative Commons Attribution
    4.0 International License (CC BY 4.0).
  \end{block}
